Online {\IterComp}

### 2017-11-17 results.tex
Exp.Setup pointer to online search results
search is now subsection
tiny

\subsubsection{Cost Evaluation During the Online Search}

@@

Figure~\ref{fig:deployment_cost} shows, for each benchmark and configuration, the speedup over \texttt{-O3} of the best optimization sequence
evaluated by the search but also the average profitability/cost experienced by the user throughout the search process (labeled as [Live]),
which takes into account the overhead of the work profiling. We evaluate three configurations that use work profiling, namely \OptProf,
\WCRelax-5\%, and \WPRelax-5\%. By widening the search space, we are able to improve performance significantly compared to the results in
Figure~\ref{fig:speedups}. In terms of the overall speedup throughout the search, all three configurations are profitable on average. 
Although there is a slight risk we select a suboptimal version and the user experiences slowdown, our genetic search focuses on promising
optimization sequences, reducing the risk of selecting a suboptimal version of the program as the genetic population evolves. For all three
configurations, after the first generation, the optimization sequences we evaluate tend to overcome this issue, with their benefits
surpassing the profiling overheads. This is particularly true for \WPRelax-5\%, where the small overhead combined with the large speedup
lead to a 7.3\% overall speedup.

>>>>

\subsection{Overall Benefit of Online Search}\label{subsec:search}

@@

Figure~\ref{fig:deployment_cost} shows, for each benchmark and configuration, the speedup over \texttt{-O3} of the best optimization sequence
evaluated by the search but also the average profitability/cost experienced by the user throughout the search process (labeled as [Live]),
which takes into account the overhead of the work profiling. We evaluate three configurations that use work profiling, namely \OptProf,
\WCRelax-5\%, and \WPRelax-5\%. By widening the search space, we are able to improve performance significantly compared to the results in
Figure~\ref{fig:speedups}. In terms of the overall speedup throughout the search, all three configurations are profitable on average. 
Although there is a slight risk we select a suboptimal version and the user experiences slowdown, our genetic search focuses on promising
optimization sequences, reducing the risk of selecting a suboptimal version of the program as the genetic population evolves. For all three
configurations, after the first generation, the optimization sequences we evaluate tend to overcome this issue, with their benefits
surpassing the profiling overheads. This is particularly true for \WPRelax-5\%, where the small overhead combined with the large speedup
leads to a 7.3\% overall speedup.
